---
title: "CaseStudy"
author: "Yezhuo Li"
date: "2025-06-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 8, 
                      fig.height = 6, 
                      fig.align = 'center', 
                      dpi = 300)
```

This R Markdown document includes the codes and figures in Section 4.

```{r}
source("Scales.R")
source("Functions.R")
library(sensitivity)
library(cowplot)
library(ggplot2)
```

# Summary of Core Parameters

N--- size of grid\
M--- the number of realization\
x.sample--- initial input data\
y.sample--- initial output data\
g.sample--- initial constraint data\
d--- d-dimension of input variable\
lb--- lower bound - vector\
ub--- upper bound - vector\
g_constraint--- constraint threshold\
Sensitivity Analysis--- Run Sobol' Analysis Using Saltelli's Scheme

```{r}
lb <- c(125, 150, 600, 7200)
ub <- c(180, 180, 6600, 12000) 
eps <- sqrt(.Machine$double.eps)
g_constraint <- 0.96
d <- 4
initial_sample_size <- 50
N <- 500 
M <- 10000
```

#### Load Cure Process Data

```{r}
load("Q22.Rdata")
x.sample <-Q22[,1:4]
y.sample <- Q22[,5]
g.sample <- Q22[,6]
```

# Decision Uncertainty Experiment: Optimal Decision Uncertainty & Sensativity Analysis (Section 4)

```{r}
set.seed(123)
result_gp <- gp_opts_constraint(x.sample, y.sample, g.sample, g_constraint, lb, ub, N, M, d)
x_gp <- result_gp$gp.xhat
y_gp <- result_gp$gp.yhat
g_gp <- result_gp$gp.ghat
surrogate_y <- function(X){result_gp$gpm_y(X)$mean}
surrogate_g <- function(X){result_gp$gpm_g(X)$mean}

opt_mean <- gp_opt_mean_constraint(x.sample, y.sample, g.sample, g_constraint, lb, ub)
opt_true_A <- c(opt_mean[3]/60,opt_mean[1])
opt_true_B <- c(opt_mean[4]/60,opt_mean[2])
```

#### Plot Optimal Decision Uncertainty (Figure 4 in Section 4)

```{r}
aa=rbind(cbind(x_gp[ ,2], x_gp[ ,4]/60), cbind(x_gp[,1], x_gp[,3]/60))
df_plot <- data.frame(Time=aa[,2], Temperature=aa[,1])

custom_breaks <- c(0, 0.00005, 0.0001, 0.00015, 0.0002, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1)
ggplot(df_plot, aes(x = Time, y = Temperature)) +
  geom_density_2d_filled(aes(fill = ..level..), breaks = custom_breaks) +
  scale_fill_brewer(palette = "PuBu", name = "Density Level") +  
  geom_point(aes(x = opt_true_A[1], y = opt_true_A[2]), color = "red", size = 2.5) +
  geom_point(aes(x = opt_true_B[1], y = opt_true_B[2]), color = "red", size = 2.5) +
  geom_segment(aes(x = 7.5, y = 140, xend = opt_true_A[1], yend = opt_true_A[2]), color = "red") +
  geom_segment(aes(x = opt_true_A[1], y = opt_true_A[2], xend = opt_true_B[1], yend = opt_true_B[2]), color = "red") +
  geom_segment(aes(x = opt_true_B[1], y = opt_true_B[2], xend = 200.385, yend = 140), color = "red") +
  ylim(140, 185) +
  xlim(0, 205) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.margin = unit(c(0.5, 3, 0.5, 3), "cm")
  ) +
  labs(x = "Time", y = "Temperature")
```

#### Compute Sensitivity Scores

```{r}
X1 <- x_gp[1:(M/2), ]
X2 <- x_gp[(M/2+1):M, ]
sobol_result <- sobolSalt(model = surrogate_y, X1, X2, scheme="A", nboot = 100)

ss_effects_gp <- c(sobol_result$S$original, sobol_result$T$original)
ss_effects_gp[ss_effects_gp < 0] <- 0 
ss_effects_gp[ss_effects_gp > 1] <- 1 
```

##### Plot Sensitivity Analysis Result From Decision Uncertainty Experiment (Figure 5 in Section 4)

```{r}
sens_gp <- data.frame(X=rep(colnames(x.sample), 2), value = ss_effects_gp, 
                      group = rep(c("Sobol' First-Order Indices", 
                                    "Sobol' Total Sensitivity Indices"), 
                                  each=length(ss_effects_gp)/2))

p_gp.opt <- ggplot(sens_gp, aes(x = X, y = value)) +
  geom_col(aes(fill = group), position = "dodge") +
  geom_text(aes(label = sprintf("%.4f", value)), position = position_dodge2(width = 0.8), 
            vjust = -0.2, size = 3) +  
  geom_point(data = subset(sens_gp, group == "First"), 
             position = position_dodge(width = 0.8), size = 4) +
  geom_point(data = subset(sens_gp, group == "Total"), 
             position = position_dodge(width = 0.8), size = 4) +
  scale_color_manual(values = c("#0073C2FF", "#EFC000FF"), name = " ") +
  scale_fill_manual(values = c("#0073C2FF", "#EFC000FF"), name = " ") +
  scale_y_continuous(limits = c(0, 1)) +  
  labs(title = "Decision Uncertainty", x=NULL, y=NULL) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top",
        legend.title = element_text(size = 8),
        axis.text = element_text(size = 9)) 
print(p_gp.opt)
```

# Uniform Experiment: Sensativity Analysis (Section 4)
#### Compute Sensitivity Scores
```{r}
set.seed(123)
xu1 <- randomLHS(M, 4)
xu2 <- randomLHS(M, 4)
xo1 <- scale_to_org(xu1, lb, ub)
xo2 <- scale_to_org(xu2, lb, ub)
xo1_feasible <- xo1[which(surrogate_g(xo1)>g_constraint), ][1:M/2, ]
xo2_feasible <- xo2[which(surrogate_g(xo2)>g_constraint), ][1:M/2, ]

ss_uniform <- sobolSalt(model = surrogate_y, xo1_feasible, xo2_feasible, scheme="A", nboot = 100)
ss_effects_uniform <- c(ss_uniform$S$original, ss_uniform$T$original)
ss_effects_uniform[ss_effects_uniform < 0] <- 0
ss_effects_uniform[ss_effects_uniform > 1] <- 1
```

##### Plot Sensitivity Analysis Result From Uniform Experiment (Figure 5 in Section 4)
```{r}
sens_uniform <- data.frame(X=rep(colnames(x.sample), 2), value = ss_effects_uniform, 
                           group = rep(c("Sobol' First-Order Indices", 
                                         "Sobol' Total Sensitivity Indices"),
                                       each=length(ss_effects_uniform)/2))

plot_uniform <- ggplot(sens_uniform, aes(x = X, y = value)) +
  geom_col(aes(fill = group), position = "dodge") +
  geom_text(aes(label = sprintf("%.4f", value)), position = position_dodge2(width = 0.8), 
            vjust = -0.2, size = 3) +  
  geom_point(data = subset(sens_uniform, group == "First"), 
             position = position_dodge(width = 0.8), size = 4) +
  geom_point(data = subset(sens_uniform, group == "Total"),
             position = position_dodge(width = 0.8), size = 4) +
  scale_color_manual(values = c("#0073C2FF", "#EFC000FF"), name = " ") +
  scale_fill_manual(values = c("#0073C2FF", "#EFC000FF"), name = " ") +
  scale_y_continuous(limits = c(0, 1)) +  
  labs(title = "Uniform", x=NULL, y=NULL) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top",
        axis.text = element_text(size = 9)) 
print(plot_uniform)
```

## Combined Plot (Figure 5 in Section 4)
```{r}
p<- combined_plot <- plot_grid(plot_uniform, p_gp.opt, labels = c("", ""), nrow = 1) 
ggsave("sa_4D_1.jpeg", p, width = 16, height = 6, dpi = 300)
print(combined_plot)
```
